### 2018-08-08 Sections/classical_networking_protocols.tex
floats
Indexing

There have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel switching}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet-switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collision detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

@@

\subsubsection{Internet Protocol} \index{Internet Protocol}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{ethernet}
	\caption{The topology of an Ethernet network, whereby all users share a common channel, which they can broadcast to at their leisure. If data packets collide, it is detected via the packets' checksums, and the corrupted packets may be re-broadcast after a random `backoff' waiting period, repeating this process until packet delivery is successful. Obviously the chance of collisions occurring increases with the number of connected users, thus network performance is inversely related to the number of nodes.} \label{fig:ethernet}
\end{figure}

@@

To mitigate the need for a central authority, nodes engage in only nearest neighbour communication, sharing their routing tables with one another, to query about the distance metrics (Sec.~\ref{sec:costs}) associated with routes to different destinations. This communication is taking place regularly, and as nodes' routing tables become populated, updating in real-time, they will (hopefully) reach a steady-state. From these tables, single-source shortest path algorithms (Sec.~\ref{sec:single_source_sp}) can be applied by nodes to construct a complete picture of costs to every point in the network. Such a nearest neighbour algorithm is effectively a distributed breadth-first-search\index{Breadth-first-search} algorithm (Sec.~\ref{sec:path_exp}).

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{network_hierarchy}
	\caption{Simple example of a network with two levels in its hierarchy. At the lowest level are 4 different subnets belonging to different departments within an organisation, each of which implements Ethernet networking. Above this, the subnets connect together in a star network via a central router. By subdividing the network hierarchy as such, if most traffic emanating within a subnet stays within that same subnet, collisions between packets on different subnets are avoided, thereby improving the efficiency of the subnets' Ethernet implementations.} \label{fig:net_hierarchy}
\end{figure}

>>>>

There have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet-switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collision detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

@@

\subsubsection{Internet Protocol} \index{Internet Protocol (IP)}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.47\textwidth]{ethernet}
	\caption{The topology of an Ethernet network, whereby all users share a common channel, which they can broadcast to at their leisure. If data packets collide, it is detected via the packets' checksums, and the corrupted packets may be re-broadcast after a random `backoff' waiting period, repeating this process until packet delivery is successful. Obviously the chance of collisions occurring increases with the number of connected users, thus network performance is inversely related to the number of nodes.} \label{fig:ethernet}
\end{figure}

@@

To mitigate the need for a central authority, nodes engage in only nearest neighbour communication, sharing their routing tables with one another, to query about the distance metrics (Sec.~\ref{sec:costs}) associated with routes to different destinations. This communication is taking place regularly, and as nodes' routing tables become populated, updating in real-time, they will (hopefully) reach a steady-state. From these tables, single-source shortest path algorithms (Sec.~\ref{sec:single_source_sp}) can be applied by nodes to construct a complete picture of costs to every point in the network. Such a nearest neighbour algorithm is effectively a distributed breadth-first-search\index{Breadth-first-search (BFS) algorithm} algorithm (Sec.~\ref{sec:path_exp}).

@@

\begin{figure}[htpb]
	\includegraphics[width=0.47\textwidth]{network_hierarchy}
	\caption{Simple example of a network with two levels in its hierarchy. At the lowest level are 4 different subnets belonging to different departments within an organisation, each of which implements Ethernet networking. Above this, the subnets connect together in a star network via a central router. By subdividing the network hierarchy as such, if most traffic emanating within a subnet stays within that same subnet, collisions between packets on different subnets are avoided, thereby improving the efficiency of the subnets' Ethernet implementations.} \label{fig:net_hierarchy}
\end{figure}

### 2018-08-08 Sections/cryptowars.tex
floats
Indexing

Today there are countless freely available private-key cryptographic protocols available online, and some have been standardised by standards institutes. Currently, the Advanced Encryption Standard (AES) is a standard endorsed by the US government, replacing the earlier standardised Data Encryption Standard (DES)\index{Data encryption standard} whose mere 56-bit key-length is today considered insecure. AES is a block cipher\index{Block cipher}, meaning that it divides data into small blocks of 128 bits, each of which are encrypted independently, and operates with key lengths of up to 256 bits, making it very robust against (even quantum) brute-force attacks (Sec.~\ref{sec:attacks_on_class}). The length of the plaintext and ciphertext is the same, meaning there is no bandwidth overhead when communicating encrypted data across a network.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function RSAGenerateKey():
\begin{enumerate}
\item $p$ = randomPrime()
\item $q$ = randomPrime()
\item if($p=q$) goto 1
\item $n = pq$
\item $\lambda = \mathrm{lcm}(p-1,q-1)$
\item $e = \mathrm{coprime}(\lambda) \,\,\mathrm{s.t} \,\,e<\lambda$
\item $d = e^{-1}\,(\mathrm{mod} \, \lambda)$
\item publicKey = $\{n,e\}$
\item privateKey = $\{n,d\}$
\item keyPair = \{publicKey,privateKey\}
\item return(keyPair)
\item $\Box$	
\end{enumerate}
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item $\mathtt{cipertext} = \mathtt{plaintext}^e \, (\mathrm{mod} \, n$)
\item return(ciphertext)
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item $\mathtt{plaintext} = \mathtt{ciphertext}^d \, (\mathrm{mod} \, n)$
\item return(plaintext)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Number-theoretic algorithms based on modular arithmetic for RSA key generation, encryption and decryption.} \label{alg:RSA}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DigitalSignature(message,keyPair):
\begin{enumerate}
\item Alice prepares a short \textit{digest}\index{Digest} of her message using a cryptographic hash function\index{Hash function}, such as SHA256\index{SHA256} (Sec.~\ref{sec:hashing}),\\
	\vspace{1mm} 
	$digest=SHA256(message)$
	\item Alice encrypts the digest using her private key. This forms the `digital signature',\\
	\vspace{1mm} 
	$signature = RSAEncrypt(digest,privateKey)$
	\item Alice transmits the digital signature and original message to Bob,\\
	\vspace{1mm} 
	$signedMessage = \{message,signature\}$
	\item Bob hashes the received message,\\
	\vspace{1mm} 	
	$hash=SHA256(message)$
	\item Bob uses Alice's public-key to decrypt her digital signature,\\
	\vspace{1mm} 
	$decryptedHash =$\\
	$RSADecrypt(signature,publicKey)$
	\item Bob compares his calculated hash with Alice's decrypted hash for consistency. If the two hashes are identical, Bob concludes the message was authentic,\\
	\vspace{1mm} 
	$if(decryptedHash=hash)$\\
	$\,\,return(pass)$\\
	$else$\\
	$\,\,return(fail)$
	\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for digitally signing a message using public-key cryptography (RSA) and a cryptographic hash function (SHA256).} \label{alg:dig_sig}
\end{table}

@@

Because RSA-encrypted messages are long, digital signature protocols do not sign the full document directly. Instead they create a message digest\index{Message digest} of the document using a cryptographic hash function, which is signed using RSA. These hash functions have the property that they cannot for forged or manipulated, providing an accurate summary of a document, but with extremely low memory overhead (256 bits is typical). Hash functions are discussed next in Sec.~\ref{sec:hashing}.

@@

The most obvious approach to cracking a cryptosystem is to systematically try out all possible keys until we find one that correctly decodes the encrypted message. This is also the most na\"ive approach, and one which is computationally intractable for real-world key lengths. Specifically, for a key length of $k$ bits (\mbox{$k=256$} for AES), there are $2^k$ possible keys to try, and on average we will wait for $2^{k-1}$ trials before choosing the right one. Clearly an average waiting time of $2^{255}$ is not plausible!

@@

\subsubsection{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attacks}

@@

In the case of private-key cryptosystems such as AES, no quantum-enhanced cryptanalytic techniques have been described, which offer an exponential enhancement. Thus, modulo doubling key-lengths to counter a Grover attack, these cryptosystems are not regarded as being compromised by quantum computing.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{BB84_example}
\caption{Example execution of the BB84 protocol for securely sharing random bit-strings between Alice and Bob as per Alg.~\ref{alg:bb84}. At the conclusion of the protocol, some bits are discarded (X), with those remaining guaranteed to be secret between the two parties.} \label{fig:BB84_example}	
\end{figure}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function E91():
\begin{enumerate}
\item A central server shares a Bell pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CVQKD():
\begin{enumerate}
\item Alice chooses two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\mathrm{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\mathrm{mod}),
\end{align}
where $V_\mathrm{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent \comment{I don't get this, Alice is deterministically encoding x+ip, where's the randomness in the choice of basis? Are we adding a randomised phase that puts us into a diagonal basis sometimes, or something like that}
\item \comment{Complete the rest of this}
\end{enumerate}}
\end{mdframed}
\caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

@@

The best known attack against photonically implemented BB84 is the `photon-number splitting attack'\index{Photon-number splitting attack}. This attack targets implementations where Alice's photon source does not produce perfect single-photon states, but may have some amplitude of higher photon-number. Weak coherent states or SPDC states exhibit this property. The attack is very simple. Eve simply performs a man-in-the-middle attack\index{Man-in-the-middle attack}, but not of an intercept-resend\index{Intercept-resend attack} variety. Rather than intercepting the entire channel, she inserts a low reflectivity beamsplitter and measures only the reflected mode, the other following its desired trajectory to Bob. Now there is a chance that Eve can extract just one of the multiple photons in the signal, such that Bob still receives a photon. Eve holds the split-off signal in memory until the classical communication of encoding bases, at which point she measures all her split signals in the correct basis.

@@

As discussed, the RSA public-key cryptosystem is vulnerable to an efficient quantum attack, whereas private-key schemes like AES are not (believed to be). Thus, combining QKD schemes with private-key classical schemes does not compromise security in the quantum era.

@@

In the near future, as QKD schemes begin their rollout in space and on Earth, random bits from the QKD implementation will be very expensive and exhibit low bandwidth. Suppose we wanted to securely videoconference across the globe. For just a single user this would require megabits per second of shared random bits, which will quickly saturate the capacity of overhead quantum satellites. Instead, let us use the QKD system to securely share just a 256-bit private session key\index{Session key} between two users. This is subsequently employed for AES256 encryption that operates entirely over the classical network, which we regard as extremely cheap. Importantly, unlike one-time pad implementations, this session key may be reused. Now we have a hybrid system which is not quantum-compromised, but which overcomes the cost and bandwidth issues associated with upcoming QKD networks.

@@

\begin{figure*}[!htb]
\includegraphics[width=0.8\textwidth]{QAB}
\caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover.} \label{fig:QAB}
\end{figure*}

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n}+\ket{1}^{\otimes n})$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

>>>>

Today there are countless freely available private-key cryptographic protocols available online, and some have been standardised by standards institutes. Currently, the Advanced Encryption Standard (AES)\index{Advanced Encryption Standard (AES)} is a standard endorsed by the US government, replacing the earlier standardised Data Encryption Standard (DES)\index{Data Encryption Standard (DES)} whose mere 56-bit key-length is today considered insecure. AES is a block cipher\index{Block cipher}, meaning that it divides data into small blocks of 128 bits, each of which are encrypted independently, and operates with key lengths of up to 256 bits (referred to as AES256), making it very robust against (even quantum) brute-force attacks (Sec.~\ref{sec:attacks_on_class}). The length of the plaintext and ciphertext is the same, meaning there is no bandwidth overhead when communicating encrypted data across a network.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function RSAGenerateKey():
\begin{enumerate}
\item $p$ = randomPrime()
\item $q$ = randomPrime()
\item if($p=q$) goto 1
\item $n = pq$
\item $\lambda = \mathrm{lcm}(p-1,q-1)$
\item $e = \mathrm{coprime}(\lambda) \,\,\mathrm{s.t} \,\,e<\lambda$
\item $d = e^{-1}\,(\mathrm{mod} \, \lambda)$
\item publicKey = $\{n,e\}$
\item privateKey = $\{n,d\}$
\item keyPair = \{publicKey,privateKey\}
\item return(keyPair)
\item $\Box$	
\end{enumerate}
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item $\mathtt{cipertext} = \mathtt{plaintext}^e \, (\mathrm{mod} \, n$)
\item return(ciphertext)
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item $\mathtt{plaintext} = \mathtt{ciphertext}^d \, (\mathrm{mod} \, n)$
\item return(plaintext)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Number-theoretic algorithms based on modular arithmetic for RSA key generation, encryption and decryption.} \label{alg:RSA}
\end{table}

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DigitalSignature(message,keyPair):
\begin{enumerate}
\item Alice prepares a short \textit{digest}\index{Digest} of her message using a cryptographic hash function\index{Hash functions}, such as SHA256\index{SHA256} (Sec.~\ref{sec:hashing}),\\
	\vspace{1mm} 
	$digest=SHA256(message)$
	\item Alice encrypts the digest using her private key. This forms the `digital signature',\\
	\vspace{1mm} 
	$signature = RSAEncrypt(digest,privateKey)$
	\item Alice transmits the digital signature and original message to Bob,\\
	\vspace{1mm} 
	$signedMessage = \{message,signature\}$
	\item Bob hashes the received message,\\
	\vspace{1mm} 	
	$hash=SHA256(message)$
	\item Bob uses Alice's public-key to decrypt her digital signature,\\
	\vspace{1mm} 
	$decryptedHash =$\\
	$RSADecrypt(signature,publicKey)$
	\item Bob compares his calculated hash with Alice's decrypted hash for consistency. If the two hashes are identical, Bob concludes the message was authentic,\\
	\vspace{1mm} 
	$if(decryptedHash=hash)$\\
	$\,\,return(pass)$\\
	$else$\\
	$\,\,return(fail)$
	\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for digitally signing a message using public-key cryptography (RSA) and a cryptographic hash function (SHA256).} \label{alg:dig_sig}
\end{table}

@@

Because RSA-encrypted messages are long, digital signature protocols do not sign the full document directly. Instead they create a message digest\index{Message digests} of the document using a cryptographic hash function, which is signed using RSA. These hash functions have the property that they cannot for forged or manipulated, providing an accurate summary of a document, but with extremely low memory overhead (256 bits is typical). Hash functions are discussed next in Sec.~\ref{sec:hashing}.

@@

The most obvious approach to cracking a cryptosystem is to systematically try out all possible keys until we find one that correctly decodes the encrypted message. This is also the most na\"ive approach, and one which is computationally intractable for real-world key lengths. Specifically, for a key length of $k$ bits (\mbox{$k=256$} for AES256), there are $2^k$ possible keys to try, and on average we will wait for $2^{k-1}$ trials before choosing the right one. Clearly an average waiting time of $2^{255}$ is not plausible!

@@

\subsubsection{Brute-force}\index{Brute-force}\label{sec:brute_force_attacks}

@@

In the case of private-key cryptosystems such as AES\index{Advanced Encryption Standard (AES)}, no quantum-enhanced cryptanalytic techniques have been described, which offer an exponential enhancement. Thus, modulo doubling key-lengths to counter a Grover attack, these cryptosystems are not regarded as being compromised by quantum computing.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

\begin{figure}[htpb]
\includegraphics[width=0.47\textwidth]{BB84_example}
\caption{Example execution of the BB84 protocol for securely sharing random bit-strings between Alice and Bob as per Alg.~\ref{alg:bb84}. At the conclusion of the protocol, some bits are discarded (X), with those remaining guaranteed to be secret between the two parties.} \label{fig:BB84_example}	
\end{figure}

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function E91():
\begin{enumerate}
\item A central server shares a Bell pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CVQKD():
\begin{enumerate}
\item Alice chooses two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\mathrm{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\mathrm{mod}),
\end{align}
where $V_\mathrm{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent \comment{I don't get this, Alice is deterministically encoding x+ip, where's the randomness in the choice of basis? Are we adding a randomised phase that puts us into a diagonal basis sometimes, or something like that}
\item \comment{Complete the rest of this}
\end{enumerate}}
\end{mdframed}
\caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

@@

The best known attack against photonically implemented BB84 is the `photon-number splitting attack'\index{Photon-number splitting attack}. This attack targets implementations where Alice's photon source does not produce perfect single-photon states, but may have some amplitude of higher photon-number. Weak coherent states or SPDC states exhibit this property. The attack is very simple. Eve simply performs a man-in-the-middle attack\index{Intercept-resend attack}, but not of an intercept-resend\index{Intercept-resend attack} variety. Rather than intercepting the entire channel, she inserts a low reflectivity beamsplitter and measures only the reflected mode, the other following its desired trajectory to Bob. Now there is a chance that Eve can extract just one of the multiple photons in the signal, such that Bob still receives a photon. Eve holds the split-off signal in memory until the classical communication of encoding bases, at which point she measures all her split signals in the correct basis.

@@

As discussed, the RSA public-key cryptosystem is vulnerable to an efficient quantum attack, whereas private-key schemes like AES\index{Advanced Encryption Standard (AES)} are not (believed to be). Thus, combining QKD schemes with private-key classical schemes does not compromise security in the quantum era.

@@

In the near future, as QKD schemes begin their rollout in space and on Earth, random bits from the QKD implementation will be very expensive and exhibit low bandwidth. Suppose we wanted to securely videoconference across the globe. For just a single user this would require megabits per second of shared random bits, which will quickly saturate the capacity of overhead quantum satellites. Instead, let us use the QKD system to securely share just a 256-bit private session key\index{Session key} between two users. This is subsequently employed for AES256\index{Advanced Encryption Standard (AES)} encryption that operates entirely over the classical network, which we regard as extremely cheap. Importantly, unlike one-time pad implementations, this session key may be reused. Now we have a hybrid system which is not quantum-compromised, but which overcomes the cost and bandwidth issues associated with upcoming QKD networks.

@@

\begin{figure*}[htpb]
\includegraphics[width=0.8\textwidth]{QAB}
\caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover.} \label{fig:QAB}
\end{figure*}

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n}+\ket{1}^{\otimes n})$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}
